Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-07-30 paper/paper.results.tex
Start simulations section

\subsection{Simulations}

>>>>

\subsection{Simulations}
In this section, we want to analyze properties of the LP problem on simulated data. Our goal is to see whether the aforementioned formulation of the problem is going to suffer from run-time issues, when presented with a large set of constraints arising from a hypothetical department with many clinicians, or clinicians with many time-off requests throughout the year. We also want to analyze the behaviour of the LP problem when applied to a longer time horizon than just a single year.
